% the acknowledgments section

\newthought{Though many regard the PhD as a solitary endeavor} (and it has certainly felt that way during my last few weeks of writing), in my experience that couldn't be farther from the truth. I have gone through a graduate program at an institution I didn't even dream of attending while growing up; this document and this experience have only been possible because of the support, encouragement, and love of many people.\\

I have had the great privilege to work with not one, but two incredible advisors during my time at Yale. I thank Professor Keith Baker for always believing in me, helping me to learn and grown as a scientist, and encouraging me during the most difficult periods of this journey. I thank Professor Sarah Demers for being the kind of person someone dreams of having advise their thesis; thank you for helping me build a research path I love, for all the work you do in this department, ATLAS, and beyond, and for being an incredible mentor and role-model as a scientist and woman. I also thank Professor Thomas Appelquist and Professor Bonnie Flemming for serving on my thesis committee. Thank you to my UChicago physics family, Young-kee, David, Bjoern, Yangyang, and Jeff, for building my foundations and giving me a second home at CERN.\\

I'm grateful to the colleagues I have worked with during the past five years for inspiring me with their dedication and brilliant ideas. I have the deepest admiration for Joey Riechert and Lucas Flores and appreciate all the time we spent working on electrons together. Similarly, I thank Eleonora Benhar for being the best post-doc I could have ever asked for during those years. Thank you to my research group Mariel, Emma, and Lotte for owning this analysis and battling the xTau Framework with me.\\

Thank you to all my dear friends in ATLAS and CERN: its been a joy to learn with you, make change, and see the world. I am especially thankful for my angry lady crew, Julia, Lesya, Leo, Jennet, and Rachel; you are all bad-asses and the physics would is lucky to have you. Thank you to the two people who have been like my ATLAS older siblings, Micky and Dan; I can't begin to express how much you both have done for me. Dan, you single-handedly talked me out of dropping out and Micky, I honestly don't know who I would be as a physicist and ML practitioner without you.

Thank you to all the people who have made New Haven feel like home over the past years. Kat, Kelly, Yuri, Josh, Darryl, Danny, Deeha, Matt, Margot, Zak, and so many others. I'm thankful to have been a part of communities full of beautiful individuals: The Grad Women's Rugby Team, Danceworks, and Senate.

I extend my deepest gratitude to all the people in IOP, DBT, and MHC who have spent the time to help me heal and grow; thank you to Frances Addachi, Kelly Workman, Ashley Heely, Emily Cooley, and Ryan Wallace. Above all, thank you to Paul Hoffman, you words and work will remain with me for the rest of my life.

I am grateful to my parents for always providing opportunities for me to grow, explore, and chase my dreams. I thank my father for reminding me that education is the one thing no one can take away from you and my mother for showing me how to teach and how to learn. To my sister, thank you for always being proud of me and for showing me it's ok to forge your own path. I also thank the artists whose words I've included in these chapters for giving me a connection to home even when I'm far away. 

To my best friends, Annina, Nataly, and Annie, it took all four of us to get me through this journey. You may not have helped me with QFT homework or edited my conference slides, but I can say with absolute certainty that I would not be here without each of you. I love you so much. 

Finally, thank you to Sohan. You have held my hand through the lowest points of my life, loved me when I didn't deserve it, and never stopped believing in me. And always told me how smart I was (for an experimentalist). 

\begin{displayquote}
We do not believe in ourselves until someone reveals that deep inside us something is valuable, worth listening to, worthy of our trust, sacred to our touch. Once we believe in ourselves we can risk curiosity, wonder, spontaneous delight or any experience that reveals the human spirit.
\qauthor{E. E. Cummings}
\end{displayquote}